### 2017-09-06 paper/related.tex

\section{Related Work}
\label{sec:related}
Researchers and practitioners have been shedding light to the to the
demand of techniques for optimizing test execution. For instance, a
recent paper from the automotive industry reported that test suites
can take days to run~\cite{artl-etal-icst2015}.  There are different
aspects to consider when dealing with the challenge of reducing
test cost.

\textit{Test Selection vs. Parallelism:}
Research has focused mostly on test suite minimization,
prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
Most of these techniques are unsound (\ie{}, they do not guarantee
that fault-revealing tests will be selected), however, more recently,
sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
computes which tests have been impacted by changes.  A test is
discarded for execution if it does not depend on any changed file
dynamically reachable from execution. Although Ekstazi is focused on
regression test selection, it highlights the importance of parallelism
as a complement to test selection.  In fact, as in their evaluation, we
also discovered subjects with parallelism enabled by default.  Test
suite parallelization is complementary to regression testing
techniques.

\Jbc{
\textit{Usage of massively parallel hardware:}
Previous research investigated the feasibility of testing embedded
software on Graphics Processing Units (GPUs) as an alternative
to multicore CPUs~\cite{rajan-etal-ase2014}.
The Simple Instruction Multiple Data (SIMD) architecture of
modern GPUs allows running the same test case with different test data
over several threads.
Although benchmarks indicate far superior performance over traditional
multicore CPUs, existing GPU programming-models (\eg,
CUDA~\cite{cuda}, and OpenCL~\cite{opencl}) are compatible only with a
subset of the C/C++ language.
Recent work proposed a compiler-assisted approach to make programs
compatible with the relying programming
model~\cite{yaneva-etal-issta2017}; however, }\Jbc{...Justify they are out
of scope for our subjects...}.

>>>>

\section{Related Work}
\label{sec:related}
Researchers and practitioners have been shedding light to the demand
of techniques for optimizing test execution.

%% For instance, a recent paper from the automotive industry reported
%% that test suites can take days to run~\cite{artl-etal-icst2015}.
%% There are different aspects to consider when dealing with the
%% challenge of reducing test cost.

\textit{Test Selection:}
Research has focused mostly on test suite minimization,
prioritization, reduction, and selection~\cite{yoo-harman-stvr2012}.
Most of these techniques are unsound (\ie{}, they do not guarantee
that fault-revealing tests will be selected), however, more recently,
sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi~\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
computes which tests have been impacted by changes.  A test is
discarded for execution if it does not depend on any changed file
dynamically reachable from execution. Although Ekstazi is focused on
regression test selection, it highlights the importance of parallelism
as a complement to test selection.  In fact, as in their evaluation, we
also discovered subjects with parallelism enabled by default.  Test
suite parallelization is complementary to regression testing
techniques.

%% \textit{Usage of massively parallel hardware:}
\textit{Hardware level parallelization:} Previous research
investigated the feasibility of testing embedded software on Graphics
Processing Units (GPUs) as an alternative to multicore
CPUs~\cite{rajan-etal-ase2014}.  The Simple Instruction Multiple Data
(SIMD) architecture of modern GPUs allows running the same test case
with different test data over several threads.  Although benchmarks
indicate far superior performance over traditional multicore CPUs.
%% , existing GPU programming-models (\eg{}, CUDA~\cite{cuda}, and
%% OpenCL~\cite{opencl}) are compatible only with a subset of the C/C++
%% language.
Recent work proposed a compiler-assisted approach to make
programs compatible with the relying programming
model~\cite{yaneva-etal-issta2017};

\Jbc{...Justify they are out of scope for our subjects...}.
